DRAFT: Social Learning and Shared Belief: The Importance of Bias and Trust for Information Diffusion

### 2014-07-11 paper/paper.tex
fix alpha and beta appendix
take care of gamma
phi and theta

\[p(\beta_t | \phi, \beta_{t-1}, b^2, \sigma^2) \propto p(\phi | \beta_t) p(\beta_t | \beta_{t-1})\]

\[=  \prod_{k=1}^K N(\beta_t, b^2I) N(\beta_{t-1}, \sigma^2I)\]

\[\propto \exp{\left(\sum_{k=1}^K(\phi_k - \beta_{t})^T(\phi_k - \beta_{t}) + (\beta_{t} - \beta_{t-1})^T(\beta_{t} - \beta_{t-1})\right)}\]

Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.

@@

\[p(\alpha_{it} | \theta, \text{\boldmath$\alpha$}_{t-1}, \gamma_i, a^2, \delta^2) \propto p(\theta | \alpha_{it}) p(\alpha_t | \text{\boldmath$\alpha$}, \gamma_i)\]

\[= \prod_{d=1}^{D_i} N(\alpha_{it}, a^2I) N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)\]

\[\propto \exp{\left(\sum_{d=1}^{D_i}(\theta_d - \alpha_{it})^T(\theta_d - \alpha_{it}) + (\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)\right)}\]

Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.

@@

\[p(\gamma_i | \alpha_{it}, \text{\boldmath$\alpha$}_{t-1}, \mu, \xi^2) \propto p(\alpha_{it} | \text{\boldmath$\alpha$}_{t-1}, \gamma_i, \delta^2) p(\gamma_i | \mu, \xi^2)\]

\[= \prod_{t=2}^T N(\text{\boldmath$\alpha$}_{t-1}^T \gamma_i, \delta^2I)N(\mu, \xi^2)\]

\[\propto \exp{\left(\sum_{t=2}^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i)^T(\alpha_{it} - \text{\boldmath$\alpha$}_{t-1}^T \gamma_i) + (\gamma_i - \mu)^T(\gamma_i - \mu)\right)}\]

Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.

@@

\[= \prod_{d=1}^D \prod_{j=1}^{J_d} Mult(\pi(\theta_{dit}))\prod_{d=1}^D N(\alpha_{it}, \delta^2I)\]

\[\propto \left(\prod_{d=1}^D \prod_{j=1}^{J_d} \frac{\theta_{dit}^{I_{z_j}=k}}{\sum_k \theta_{dit}}\right) \exp{\left(\sum_{d=1}^D(\theta_{dit} - \alpha_{it})^T(\theta_{dit} - \alpha_{it})\right)} \]

Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.

@@

\[= \prod_{k=1}^K \prod_{j=1}^{J_k} Mult(\pi(\phi_{kt}))\prod_{k=1}^K N(\beta_t, b^2)\]

\[\propto \left(\prod_{k=1}^K \prod_{j=1}^{J_k} \frac{\phi_{kt}^{I_{w_j}=v}}{\sum_v \phi_{kt}}\right) \exp{\left(\sum_{k=1}^K(\phi_{kt} - \beta_t)^T(\phi_{kt} - \beta_t)\right)}\]

Since this doesn't have a standard form we use Metropolis Hastings to estimate the full conditional.

>>>>

\[p(\beta_t | \phi_t, \beta_{t-1}, b^2, \sigma^2) \propto \prod_{k=1}^K p(\phi_{kt} | \beta_t) p(\beta_t | \beta_{t-1})\]

\[= \prod_{k=1}^K N(\phi_{kt};\beta_t, b^2) N(\beta_{t-1}, \sigma^2)\]

\[\propto N(\mu_{\beta t}, \Lambda_{\beta t})\]

\[\Lambda_{\beta t} = ((\sigma^2)^{-1} + k (b^2)^{-1})^{-1}\]

\[\mu_{\beta t} = \Lambda_{\beta t} \left((\sigma^2)^{-1}\beta_{t-1} + k (b^2)^{-1} \sum_{k=1}^K \phi_{kt}\right) \]

@@

\[p(\alpha_{it} | \theta_{it}, \text{\boldmath$\alpha$}_{t-1}, \gamma_i, a^2, \delta^2) \propto \prod_{k=1}^K p(\phi_{kt} | \beta_t) p(\beta_t | \beta_{t-1})\]

\[= \prod_{d=1}^{D_i} N(\theta_{dit};\alpha_{it}, a^2) N(\text{\boldmath$\alpha$}_{t-1}\gamma_i, \delta^2)\]

\[\propto N(\mu_{\alpha i t}, \Lambda_{\alpha i t})\]

\[\Lambda_{\alpha i t} = ((\delta^2)^{-1} + d_i (a^2)^{-1})^{-1}\]

\[\mu_{\alpha i t} = \Lambda_{\alpha i t} \left((\delta^2)^{-1}\text{\boldmath$\alpha$}_{t-1} \gamma_i + d_i (a^2)^{-1} \sum_{d=1}^{D_i} \theta_{dit}\right) \]

@@

\[p(\gamma_i | \text{\boldmath$\alpha$}_{i}, \text{\boldmath$\alpha$}_{-1}, \eta, \xi^2) \propto p(\text{\boldmath$\alpha$}_i | \text{\boldmath$\alpha$}_{-1}, \gamma_i, \delta^2) p(\gamma_i | \eta, \xi^2)\]

\[= N(\text{\boldmath$\alpha$}_{i};\text{\boldmath$\alpha$}_{-1}^T \gamma_i, \delta^2)N(\eta, \xi^2)\]

\[\propto N(\mu_{\gamma i}, \Lambda_{\gamma i})\]

\[\Lambda_{\gamma i} = \left((\xi^2)^{-1} + \text{\boldmath$\alpha$}_{-1}^T(\delta^2)^{-1}\text{\boldmath$\alpha$}_{-1}\right)^{-1}\]

\[\mu_{\gamma i} = \Lambda_{\gamma i} \left((\xi^2)^{-1} \eta + \text{\boldmath$\alpha$}_{-1}^T(\delta^2)^{-1}\text{\boldmath$\alpha$}_{i}\right)\]

@@

\[= \prod_{d=1}^{D_i} \prod_{j=1}^{J_d} Mult(z_{jdit}; \pi(\theta_{dit}))\prod_{d=1}^{D_i} N(\alpha_{it}, \delta^2I)\]

Since this doesn't have a standard form we use a slice sampler to sample from the full conditional.

@@

\[= \prod_{k=1}^K \prod_{j=1}^{J_k} Mult(w_{jkt}; \pi(\phi_{kt}))\prod_{k=1}^K N(\beta_t, b^2)\]

Since this doesn't have a standard form we use a slice sampler to sample from the full conditional.
